Twisted 11-dimensional supergravity

### 2021-10-15 dimred.tex
big merge

\parsec[s:poisson]
The original action for Kodaira-Spencer theory posited by \cite{BCOV}\surya{which reference is BCOV} has a nonlocal kinetic term. In the BV formalism, this is codified by stipulating that the BV pairing is a degenerate odd Poisson tensor rather than an odd symplectic form. 
The Poisson kernel is given by the expression 
\[
(\div\otimes 1)\delta_{\Delta \subset X\times X} \in \left[\PV^{\bu,\bu}(X)\right]^{\hotimes 2} ,
\]
see \cite[{\S 1.4}]{CLbcov1}. 
Here, we view the $\delta$-distribution as a polyvector field using the Calabi--Yau form. 
Notice that the shifted Poisson tensor does not involve the parameter $u$ at all. 
For this reason, only the duals of a small number of fields pair nontrivially under the resulting odd BV bracket. 
%Explicitly, the above kernel pairs against the dual to 
%\[
%\Sigma^1 = \sum u^k\mu^1_k, \Sigma^2 = \sum u^k\mu^2_k\in \PV^{\bu,\bu}%(X)[[u]][2]
%\]
% by the formula 
%\[
%\int \overline{\mu}_0^1\div \overline{\mu}_0^2.
%\] 
%Here, the overlines denote the dual field in 
%\[
%(\PV^{\bu,\bu}(X)[[u]][2])^*=\PV_c^{d-\bu,d-\bu}(X)[[u]][2].
%\] 
%That is, further expanding the fields as 
%\[
%\mu_k = \sum_{i,j=1}^d\mu_k^{(i,j)}\in \PV^{i,j}
%\] 
%the expression pairs $\overline{\mu}_0^{(i,j)}$ with $\overline{\mu}_0^{(d-1-i, d-j)}$.

@@

Let $X$ be a Calabi-Yau manifold of complex dimension four. 
The $\ZZ/2$ graded complex of fields of minimal Kodaira--Spencer theory on $X$ takes the form
\beqn
\begin{tikzcd}
                        &                          &                                     & {\PV^{0,\bu}}    \\
                        &                          & {\PV^{1,\bu}} \arrow[r, "u\div"]    & {u\PV^{0,\bu}}   \\
                        & {\PV^{2,\bu}} \arrow[r, "u\div"]  & {u\PV^{1,\bu}} \arrow[r, "u\div"]   & {u^2\PV^{0,\bu}} \\
{\PV^{3,\bu}} \arrow[r, "u\div"] & {u\PV^{2,\bu}} \arrow[r, "u\div"] & {u^2\PV^{1,\bu}} \arrow[r, "u\div"] & {u^3\PV^{0,\bu}}
\end{tikzcd}.
\eeqn
Here, $u^\ell\PV^{k,i}$ is placed in parity $k + i -1 \mod 2$. 
%Denote this complex by $\cE_{mKS}(X)$. 
The classical BCOV action $I_{BCOV}$ follows from the general formula we gave above.

@@

\begin{conj}
The $SU(4)$-invariant twist of type IIA supergravity on $\RR^2\times \CC^4$ is the $\Z/2$-graded Poisson BV theory with fields \[
\alpha = \sum_n \alpha_n u^n \in \cE_{mKS}(\CC^4) \otimes \Omega^{\bu}(\RR^2).\] 
The classical interaction takes the form $I_{IIA} = \int_{\CC^4 \times \RR^2} \alpha_0^3 + {\rm higher\;order\;terms}.$
%The $L_{\infty}$ structure is the natural one on the tensor product of the cdga $\Omega^{\bu}(M)$ with the $L_{\infty}$-algebra $\cE_{mKS}$.
\end{conj}

@@

Recall that in the physical theory, the components of the $C$-field in 11d that are not supported along the M-theory circle become the components of the Ramond--Ramond 2-form of type IIA. However, as noted in \cite{CLsugra} components of Ramond--Ramond fields do not appear as fields in Kodaira--Spencer theory; rather it is components of their field strengths that appear. Since components of the $C$-field become components of $\gamma_{11d}$ in $\cE$ \surya{hopefully we can see this in the component fields section}, this suggests that we must modify our description of the twist of type IIA to include potentials for certain fields.

@@

\brian{general background on susy. Why expect 5d $\cN=1$ susy}

@@

\brian{Ingmar can you argue why this is the SU(5) twist on susy grounds?}

>>>>

\parsec[s:poisson]
The original action for Kodaira-Spencer theory posited by \cite{BCOV} has a nonlocal kinetic term. In the BV formalism, this is codified by stipulating that the BV pairing is a degenerate odd Poisson tensor rather than an odd symplectic form. 
The Poisson kernel is given by the expression 
\[
(\div\otimes 1)\delta_{\Delta \subset X\times X} \in \left[\PV^{\bu,\bu}(X)\right]^{\hotimes 2} ,
\]
see \cite[{\S 1.4}]{CLbcov1}. 
Here, we view the $\delta$-distribution as a polyvector field using the Calabi--Yau form. 
Notice that the shifted Poisson tensor does not involve the parameter $u$ at all. 
For this reason, only the duals of a small number of fields pair nontrivially under the resulting odd BV bracket. 
%Explicitly, the above kernel pairs against the dual to 
%\[
%\Sigma^1 = \sum u^k\mu^1_k, \Sigma^2 = \sum u^k\mu^2_k\in \PV^{\bu,\bu}%(X)[[u]][2]
%\]
% by the formula 
%\[
%\int \overline{\mu}_0^1\div \overline{\mu}_0^2.
%\] 
%Here, the overlines denote the dual field in 
%\[
%(\PV^{\bu,\bu}(X)[[u]][2])^*=\PV_c^{d-\bu,d-\bu}(X)[[u]][2].
%\] 
%That is, further expanding the fields as 
%\[
%\mu_k = \sum_{i,j=1}^d\mu_k^{(i,j)}\in \PV^{i,j}
%\] 
%the expression pairs $\overline{\mu}_0^{(i,j)}$ with $\overline{\mu}_0^{(d-1-i, d-j)}$.

@@

Let $X$ be a Calabi-Yau manifold of complex dimension four. 
The $\ZZ/2$ graded complex of fields of minimal Kodaira--Spencer theory on $X$ takes the form
\beqn
\begin{tikzcd}
                        &                          &                                     & {\PV^{0,\bu}}    \\
                        &                          & {\PV^{1,\bu}} \arrow[r, "u\div"]    & {u\PV^{0,\bu}}   \\
                        & {\PV^{2,\bu}} \arrow[r, "u\div"]  & {u\PV^{1,\bu}} \arrow[r, "u\div"]   & {u^2\PV^{0,\bu}} \\
{\PV^{3,\bu}} \arrow[r, "u\div"] & {u\PV^{2,\bu}} \arrow[r, "u\div"] & {u^2\PV^{1,\bu}} \arrow[r, "u\div"] & {u^3\PV^{0,\bu}}
\end{tikzcd}.
\eeqn
Denote this complex by $\cE_{mKS}(X)$. 
Here, $u^\ell\PV^{k,i}$ is placed in parity $k + i -1 \mod 2$. 
%Denote this complex by $\cE_{mKS}(X)$. 
The classical BCOV action $I_{BCOV}$ follows from the general formula we gave above.

@@

\begin{conj}
The $SU(4)$-invariant twist of type IIA supergravity on $\RR^2\times \CC^4$ is the $\Z/2$-graded Poisson BV theory with fields 
\beqn\label{eqn:IIAfields}. 
\alpha = \sum_n \alpha_n u^n \in \cE_{mKS}(\CC^4) \otimes \Omega^{\bu}(\RR^2).
\eeqn
The classical interaction takes the form $I_{IIA} = \int_{\CC^4 \times \RR^2} \alpha_0^3 + {\rm higher\;order\;terms}.$
%The $L_{\infty}$ structure is the natural one on the tensor product of the cdga $\Omega^{\bu}(M)$ with the $L_{\infty}$-algebra $\cE_{mKS}$.
\end{conj}

@@

Recall that in the physical theory, the components of the $C$-field in 11d that are not supported along the M-theory circle become the components of the Ramond--Ramond 2-form of type IIA. However, as noted in \cite{CLsugra} components of Ramond--Ramond fields do not appear as fields in Kodaira--Spencer theory; rather it is components of their field strengths that appear. 
We recalled in \S \ref{s:components} that components of the $C$-field become components of $\gamma_{11d}$ in $\cE$.
This suggests that we must modify our description of the twist of type IIA to include potentials for certain fields.

@@

%\brian{general background on susy. Why expect 5d $\cN=1$ susy}

@@

%\brian{Ingmar can you argue why this is the SU(5) twist on susy grounds?}

### 2021-10-15 intro.tex
big merge

\brian{Ingmar, maybe you can comment on the status of this conjecture.}
In this paper we will provide evidence for this conjecture on a variety of fronts. 
In \S\ref{sec:susy}, we will show that this theory has all of the residual supersymmetries present after performing the holomorphic twist.

@@

Finally, we describe the non minimal twist of 11-dimensional supergravity as a background of our theory on $\CC^5 \times \RR$. 
We find a match with a con \brian{finish}
%Surprisingly, at the twisted level these symmetries

@@

In our theory there is a field which encodes this partial deformation of complex structure on the Calabi--Yau manifold $X$.
It is an even field 
\[
\mu \in \Omega^{0,1} (X , \T_X) \otimes C^\infty(S) 
\]
where $\T_X$ denotes the holomorphic tangent bundle on $X$.
Locally, $\mu$ can be decomposed as Beltrami-like differential
\[
\mu = \mu^i_j (z,\zbar, t) \d \zbar_i \frac{\partial}{\partial z_j} .
\]
Physically speaking, $\mu$ is a component of the metric which survives in the twisted theory, see \S \ref{s:component}.

@@

If we work in a background where one of $\gamma^{1,0}$ or $\gamma^{1,2}$ is zero then we see that $\mu$ is exactly a deformation of complex structure along $X$. 
In terms of the 11-dimensional geometry, this is a background which describes deformations of the natural transverse holomorphic foliation (THF structure) on $X \times S$ which further preserves the holomorphic volume form along the leaves.
We further unpack the equations of motion in other backgrounds in \S \ref{s:eom}.
%The equations of motion state that $\gamma$ is constant along $\RR$ and holomorphic along $\CC^5$. 
%Further, $\gamma$ is only defined up to the additional of a total holomorphic derivative $\gamma \sim \gamma + \del \beta$ where $\beta$ is a holomorphic function on $\CC^5$ which is constant along $\RR$.

@@

Through the dimensional reduction of our 11-dimensional theory we will find a match with Costello and Li's descriptions of twists of 10-dimensional supergravity in terms of BCOV theory.
In Table \ref{tbl:IIsugra}, we provide a summary of the conjectural twists of type IIA and type IIB supergravity. 
The notation $\CC^n_B \times \RR^{2m}_A$ uses terminology from the topological string. 
It means that the twist of supergravity we are considering arises from a certain subsector of a hybrid topological string which is the $B$-model into the Calabi--Yau manifold $\CC^n$ and the $A$-model into the symplectic manifold $\RR^{2m}$.

\begin{table}[]
\begin{tabular}{c|c|c|c|c|c|c|c|}
\cline{2-7}
& SU(5) twist & SU(4) twist & SU(3) twist & SU(2) twist & SU(1) twist & top twist  \\ \hline
\multicolumn{1}{|l|}{Type IIA} & \S \ref{s:su5IIA} & $\CC^4_B \times \RR^2_A$ & & $\CC^2_B \times \RR^6_A$ & $\begin{matrix} \text{perturbatively} \\ \text{trivial} \end{matrix}$ & $\RR^{10}_A$  \\ \hline
\multicolumn{1}{|l|}{Type IIB} & $\CC^5_B$ & & $\CC^3_B \times \RR^4_A$ & & $\CC_B \times \RR^8_A$ & \\ \hline
\end{tabular}
\end{table}

In \S \ref{s:su4red} we will show that the reduction along a line of the form $\{0\} \times \RR \times \{0\} \CC^4 \times \CC^\times \times \RR$ is equivalent to the $SU(4)$ twist of type IIA supergravity. 
The topological string approach does not lead to a description of the minimal, or holomorphic, twist of type IIA supergravity. 
In \S \ref{s:su5IIA}, we describe the reduction along the line $\{0\} \times \RR \subset \CC^5 \times \RR$ to obtain a conjectural description of the holomorphic $SU(5)$ twist of type IIA supergravity.

>>>>

%\brian{Ingmar, maybe you can comment on the status of this conjecture.}
In this paper we will provide evidence for this conjecture on a variety of fronts. 
In \S\ref{sec:susy}, we will show that this theory has all of the residual supersymmetries present after performing the holomorphic twist.

@@

Finally, we describe the non-minimal twist of 11-dimensional supergravity as a background of our theory on $\CC^5 \times \RR$. 
This non-minimal twist is invariant for the group $G_2 \times SU(2)$. 
We find a match with a conjectural description of this $G_2 \times SU(2)$ invariant twist formulated by Costello in \cite{CostelloM5} and further developed in \cite{RY}. 
%Surprisingly, at the twisted level these symmetries

\subsection*{A geometric description of the model}

@@

In our theory there is a field which encodes this partial deformation of complex structure on the Calabi--Yau manifold $X$.
It is an even field 
\[
\mu \in \Omega^{0,1} (X , \T_X) \otimes C^\infty(S) 
\]
where $\T_X$ denotes the holomorphic tangent bundle on $X$.
Locally, $\mu$ can be decomposed as Beltrami-like differential
\[
\mu = \mu^i_j (z,\zbar, t) \d \zbar_i \frac{\partial}{\partial z_j} .
\]
Physically speaking, $\mu$ is a component of the metric which survives in the twisted theory, see \S \ref{s:components}.

@@

If we work in a background where one of $\gamma^{1,0}$ or $\gamma^{1,2}$ is zero then we see that $\mu$ is exactly a deformation of complex structure along $X$. 
In terms of the 11-dimensional geometry, this is a background which describes deformations of the natural transverse holomorphic foliation (THF structure) on $X \times S$ which further preserves the holomorphic volume form along the leaves.
We further unpack the equations of motion in more general backgrounds in \S \ref{s:components}, but leave a complete study for future work.
%The equations of motion state that $\gamma$ is constant along $\RR$ and holomorphic along $\CC^5$. 
%Further, $\gamma$ is only defined up to the additional of a total holomorphic derivative $\gamma \sim \gamma + \del \beta$ where $\beta$ is a holomorphic function on $\CC^5$ which is constant along $\RR$.

@@

Through the dimensional reduction of our 11-dimensional theory we will find a match with Costello and Li's descriptions of twists of 10-dimensional supergravity in terms of BCOV theory.
In Table \ref{table:IIsugra}, we provide a summary of the conjectural twists of type IIA and type IIB supergravity. 
The notation $\CC^n_B \times \RR^{2m}_A$ uses terminology from the topological string. 
It means that the twist of supergravity we are considering arises from a certain subsector of a hybrid topological string which is the $B$-model into the Calabi--Yau manifold $\CC^n$ and the $A$-model into the symplectic manifold $\RR^{2m}$.

\begin{table}[]
\begin{tabular}{c|c|c|c|c|c|c|c|}
\cline{2-7}
& SU(5) twist & SU(4) twist & SU(3) twist & SU(2) twist & SU(1) twist & top twist  \\ \hline
\multicolumn{1}{|l|}{Type IIA} & \S \ref{s:su5IIA} & $\CC^4_B \times \RR^2_A$ & & $\CC^2_B \times \RR^6_A$ & $\begin{matrix} \text{perturbatively} \\ \text{trivial} \end{matrix}$ & $\RR^{10}_A$  \\ \hline
\multicolumn{1}{|l|}{Type IIB} & $\CC^5_B$ & & $\CC^3_B \times \RR^4_A$ & & $\CC_B \times \RR^8_A$ & \\ \hline
\end{tabular}
\caption{A summary of twists of 10-dimensional supergravity}
\label{table:IIsugra}
\end{table}

In \S \ref{s:su4red} we will show that the reduction along $\{0\} \times \RR \times \{0\} \subset \CC^4 \times \CC \times \RR$ is equivalent to the $SU(4)$ twist of type IIA supergravity. 
The topological string approach does not lead to a description of the minimal, or holomorphic, twist of type IIA supergravity. 
In \S \ref{s:su5IIA}, we describe the reduction along the line $\{0\} \times \RR \subset \CC^5 \times \RR$ to obtain a conjectural description of the holomorphic $SU(5)$ twist of type IIA supergravity.

### 2021-10-15 susy.tex
merge refs
big merge

Extensions of the supersymmetry algebra correspond to the existence of extended objects, such as branes, in the supergravity theory \brian{good reference?}. 
In 11-dimensional supersymmetry, there are two such extensions corresponding to the $M2$ brane and the $M5$ brane.
We begin by describing a less standard dg Lie algebra model for the $M2$ brane algebra.
In the next section we will explain the relationship to other descriptions in terms of $L_\infty$ algebras \cite{Basu_2005,Bagger_2007,fiorenza2015super}.

@@

Fix a rank one supercharge $Q \in S$ satisfying $Q^2 = 0$.
Such a supercharge defines the minimal twist of 11-dimensional supersymmetry. 
\brian{cite \cite{SWspinor}}
We characterize the cohomology of the algebra $\m2$ with respect to this supercharge.

@@

In this section we compare to the work of \brian{Linfty refs}.
In these references, the algebra $\m2$ is defined as an $L_\infty$  
central extension of $\lie{siso}_{11d}$.

Recall that given two spinors $\psi, \psi' \in S$ we can form the constant coefficient two-form $\Gamma_{\wedge^2} (\psi, \psi')$. 
Using this two-form we can define the following four-linear expression
\[
\mu_2 (\psi, \psi',v,v') = \<v \wedge v', \Gamma(\psi, \psi')\> .
\]
This expression is symmetric on the spinors and anti-symmetric on the vectors, therefore it defines an element in $\clie^4(\ft_{11d})$. 
In \cite{fiorenza2015super} it is shown that $\mu_2$ defines a nontrivial class in $H^4(\ft_{11d})$ so defines a one dimensional central extension of $\ft_{11d}$ as a lie 3-algebra. Instead of working with a one-dimensional central extension by $\C[2]$, we work with a central extension by the resolution $\Omega^\bullet(\R^{11})[2]$. There is a quasi-isomorphism $\clie^4(\ft_{11d})\to \clie^4(\ft_{11d}, \Omega^\bullet (\R^{11}))$ such that the induced map on cohomology identifies $\mu_2$ with the $\Omega^\bullet(\R^{11})[2]$-valued 2-cocycle we use.

>>>>

Extensions of the supersymmetry algebra correspond to the existence of extended objects, such as branes, in the supergravity theory.
In 11-dimensional supersymmetry, there are two such extensions corresponding to the $M2$ brane and the $M5$ brane.
We begin by describing a less standard dg Lie algebra model for the $M2$ brane algebra.
In the next section we will explain the relationship to other descriptions in terms of $L_\infty$ algebras \cite{Basu_2005,Bagger_2007,fiorenza2015super}.

@@

Fix a rank one supercharge $Q \in S$ satisfying $Q^2 = 0$.
Such a supercharge has a six-dimensional image in the space of (complexified) translations on $\RR^{11}$ and defines the minimal twist of 11-dimensional supersymmetry \cite{SWspinor}. 
We characterize the cohomology of the algebra $\m2$ with respect to this supercharge.

@@

In this section we compare to another description of the $M2$ brane algebra given as a one-dimensional $L_\infty$ central extension of the super Poincar\'e algebra.
Such central extensions were studied in the work \cite{BHsusyII, SSS, FSS} following \cite{CDF}.

In these references, the algebra $\m2$ is defined as an $L_\infty$  
central extension of $\lie{siso}_{11d}$. 
Recall that given two spinors $\psi, \psi' \in S$ we can form the constant coefficient two-form $\Gamma_{\wedge^2} (\psi, \psi')$. 
Using this two-form we can define the following four-linear expression
\[
\mu_2 (\psi, \psi',v,v') = \<v \wedge v', \Gamma(\psi, \psi')\> .
\]
This expression is symmetric on the spinors and anti-symmetric on the vectors, therefore it defines an element in $\clie^4(\lie{siso}_{11d})$. 
This expression defines a nontrivial class in $H^4(\lie{siso}_{11d})$ so defines a one dimensional central extension of $\lie{siso}_{11d}$ as a Lie 3-algebra. 
Instead of working with a one-dimensional central extension by $\CC[2]$, we work with a central extension by the resolution $\Omega^\bullet(\RR^{11})[2]$. There is a quasi-isomorphism $\clie^4(\lie{siso}_{11d})\to \clie^4(\lie{siso}_{11d}, \Omega^\bullet (\R^{11}))$ such that the induced map on cohomology identifies $\mu_2$ with the $\Omega^\bullet(\RR^{11})[2]$-valued two-cocycle we use.
